Virtual Memory Assisted Transactional Memory for Dynamic Languages

### 2014-06-03 talk/dls2014/paper/paper.tex
Wrong, we are describing the GC at least a bit

\item [{Write~Barrier:}] This is triggered by checking a flag in the
  header of the object.  When the flag is set, we call the slow path,
  which adds the object into the write set and unconditionally resets
  the flag.  We eagerly detect write-write conflicts by allowing only
  one transaction modifying an object at a time (by acquiring a write
  lock).\footnote{Eager write-write detection is not inherent to our
  approach; future experiments may show that we want to lift this
  restriction.}  This slow path is also responsible for privatising
  pages,\footnote{The write set contains objects, not pages.} as
  described above.  Interestingly, we are using a generational garbage
  collector (not described here) which requires a similar write barrier
  anyway -- so the same header flag is used for both cases.  The flag
  means ``something needs to be done before writing to this object'',
  and the slow path logic determines what it is.

>>>>

\item [{Write~Barrier:}] This is triggered by checking a flag in the
  header of the object.  When the flag is set, we call the slow path,
  which adds the object into the write set and unconditionally resets
  the flag.  We eagerly detect write-write conflicts by allowing only
  one transaction modifying an object at a time (by acquiring a write
  lock).\footnote{Eager write-write detection is not inherent to our
  approach; future experiments may show that we want to lift this
  restriction.}  This slow path is also responsible for privatising
  pages,\footnote{The write set contains objects, not pages.} as
  described above.  Interestingly, we are using a generational garbage
  collector (described below) which requires a similar write barrier
  anyway -- so the same header flag is used for both cases.  The flag
  means ``something needs to be done before writing to this object'',
  and the slow path logic determines what it is.
